Poisson approximate likelihood compared to the particle filter

### 2024-09-15 ms.Rnw
defer 7 to Exclude

<<maximization7-Stocks_rinit, echo=F, warning=F, message=F>>=
set.seed(12345)
sd_07 = (2/3)^6
starting_values_sbh_07 <- choose_n_fits(sbh_el_06, top_n_fits, ncores)

@@

>>>>

@@

<<maximization7-Stocks_rinit, include=FALSE>>=
set.seed(12345)
sd_07 = (2/3)^6
starting_values_sbh_07 <- choose_n_fits(sbh_el_06, top_n_fits, ncores)
